Run-Time Monitoring with Adjustable Overheads \\Using Dataflow-Guided Filtering

### 2014-09-12 related.tex
Various edits based on Ed's comments.
Updates to abstract and related work.

% Filtering
FADE \cite{fade-hpca14} presents a general filtering engine in order to reduce
the overheads of monitoring. It filters out redundant updates and null checks
by reading metadata values. 
By extending our dataflow engine for partial monitoring, we are able to also
filter out null checks as well as null metadata propagations, but we do not
handle filtering redundant updates.
% We are able to do this because the dataflow engine can also
% propagate the null information.  
In contrast to FADE, our dataflow engine only
requires reading and writing 2-bit flags rather than the entire metadata. 
% As
% we have shown, our dataflow engine also enables adjustable overheads without
% false positives which is not a capability described by FADE.

% Sampling
Statistical sampling is a method that has been applied to various debugging
techniques in order to reduce their performance overheads. For example, Liblit
et al. sampled program runs of thousands of users in order to find bugs
\cite{liblit-pldi05}. This idea has also been applied to detecting memory
leaks~\cite{chilimbi-asplos04}, dataflow analysis~\cite{greathouse-cgo11}, and
other run-time monitoring techniques. The Testudo project
\cite{testudo-micro08} specifically targets hardware-based run-time monitors.
These sampling-based techniques all limit the debugging capabilities in order
to provide lower performance overheads, similar to our architecture's goals.
However, these approaches are not able to explicitly set an overhead budget, as
our system is able to do. In addition, with the exception of Testudo, these
methods have not considered parallel monitoring. Our techniques for generally
reducing the overheads of monitoring can also be used to enable these
low-overhead, multi-user/run debugging techniques.

% Limited Monitoring
In terms of partial monitoring, the Quality Virtual Machine (QVM) is a
modification of the Java Virtual Machine (JVM) that supports run-time
monitoring with controllable overheads \cite{qvm-oopsla08}. Similarly, Huang et
al. created a framework for controlling the overheads of software-based
monitoring \cite{huang-sttt12}. These projects are targeting a similar problem
to the one we address in this paper. However, both projects are focused on
software-based monitoring and thus their mechanisms modify the software
monitoring framework in order to enable or disable monitoring. Instead, our
architecture provides a general hardware mechanism to control overheads of
parallel monitoring architectures. In addition, these works prevented
false positives by enabling and disabling monitoring using only a source-dropping
policy. Lo et al. \cite{lo-rtas14} developed a hardware architecture to limit
monitoring in hard real-time systems. Their architecture performs unrestricted 
dropping in order to guarantee strict deadlines. 
Our system allows either source-only dropping or unrestricted dropping to be performed.
This allows the designer or user to choose the appropriate policy depending on
the monitoring scheme which has not been previously explored.

>>>>

% % Filtering
% FADE \cite{fade-hpca14} presents a general filtering engine in order to reduce
% the overheads of monitoring. It filters out redundant updates and null checks
% by reading metadata values. 
% By extending our dataflow engine for partial monitoring, we are able to also
% filter out null checks as well as null metadata propagations, but we do not
% handle filtering redundant updates.
% In contrast to FADE, our dataflow engine only
% requires reading and writing 2-bit flags rather than the entire metadata.

% Sampling
Statistical sampling is a method that has been applied to various debugging
techniques in order to reduce their performance overheads. For example, Liblit
et al. sampled program runs of thousands of users in order to find bugs
\cite{liblit-pldi05}. This idea has also been applied to detecting memory
leaks~\cite{chilimbi-asplos04}, dataflow analysis~\cite{greathouse-cgo11}, and dynamic information flow tracking\cite{testudo-micro08} and
other run-time monitoring techniques. 
These sampling-based techniques all limit the debugging capabilities in order
to provide lower performance overheads, similar to our architecture's goals.
% Limited Monitoring
In terms of partial monitoring with adjustable overheads, the Quality Virtual Machine (QVM) is a
modification of the Java Virtual Machine (JVM) that supports run-time
monitoring with controllable overheads \cite{qvm-oopsla08}. Similarly, Huang et
al. created a framework for controlling the overheads of software-based
monitoring \cite{huang-sttt12}. 
Lo et al. \cite{lo-rtas14} developed a hardware architecture to limit
monitoring specifically for hard real-time systems.

Our work presents a general and efficient hardware platform to enable
partial monitoring. The architecture is designed to be applicable to a wide range of monitoring
techniques as well as monitor implementations. By studying various potential
uses of partial monitoring, including sampling for cooperative debugging and
partial protection for low overheads, we have determined important dropping
policy decisions to consider in order to best meet the requirements of the
application.

% However, these approaches are not able to explicitly set an overhead budget, as
% our system is able to do. In addition, with the exception of Testudo that is
% designed for one specific monitor, these
% methods have not considered parallel monitoring. Our techniques for generally
% reducing the overheads of monitoring can also be used to enable these
% low-overhead, multi-user/run debugging techniques.
% \ED{clarify how our approach is different. Is it more general - supporting
% a large class of monitors? Is it different because it is for parallel monitoring?
% If so, what's the significance of the parallel monitors?}

% These projects are targeting a similar problem
% to the one we address in this paper. However, both projects are focused on
% software-based monitoring and thus their mechanisms modify the software
% monitoring framework in order to enable or disable monitoring. 
% Instead, our
% architecture provides a general hardware mechanism to control overheads of
% parallel monitoring architectures, largely transparent to the original monitor. 
% In addition, these works prevented
% false positives by enabling and disabling monitoring using only a source-dropping
% policy. 
%  Their architecture performs unrestricted 
% dropping in order to guarantee strict deadlines. 
% Our system allows either source-only dropping or unrestricted dropping to be performed.
% This allows the designer or user to choose the appropriate policy depending on
% the monitoring scheme which has not been previously explored.
% \ED{Is the use of source vs. unrestricted dropping the only major difference for
% this work? That sounds rather weak.}

### 2014-09-12 title.tex
Updates to abstract and related work.

\title{
%Dataflow-Guided Filtering for Efficient and Adjustable Run-Time Monitoring
%Efficient and Adjustable Run-Time Monitoring Using Dataflow-Guided Filtering
Run-Time Monitoring with Adjustable Overheads Using Dataflow-Guided Filtering
}

@@

Recent studies have proposed various parallel run-time monitoring techniques to
improve the reliability, security, and debugging capabilities of computer
systems. However, these run-time monitors can introduce large performance and energy
overheads, especially when performed on programmable cores.
%Traditionally, these overheads have been an
%all-or-nothing cost; monitoring cannot be used if the overheads are considered
%too large.  
In this paper, we introduce a hardware dataflow tracking engine that enables
adjustable overheads through partial monitoring. This allows a trade-off to be
made between monitoring coverage and overhead. This dataflow engine
can also be extended to filter out monitoring operations associated with null
metadata in order to reduce overheads.
% In this paper, we introduce a hardware dataflow tracking engine that can be
% used to filter out unnecessary monitoring and enable adjustable partial monitoring.
% The dataflow engine can identify events with null metadata so that they can
% be filtered out. To further reduce the overhead of monitoring, we propose
% to enable a trade-off between monitoring coverage and overhead by dropping certain
% monitoring operations. For this partial monitoring, the dataflow engine is used
% to track dropped monitoring flows so that false positives can be avoided.
Given this architecture, we investigate how the dropping decisions should be
made for partial monitoring and show that there exist interesting policy
decisions which create a trade-off between closely
matching an overhead target and the coverage that can be achieved.
Our experimental results show that overheads can be reduced significantly 
by trading off coverage. For example, the proposed architecture can still
achieve 43-82\% coverage when the slowdown is reduced from 1.1-4.3x to 1.5x.
\ED{It's a bit strange to say reduced from 1.1x to 1.5x. Revise?}

>>>>

\title{
%Dataflow-Guided Filtering for Efficient and Adjustable Run-Time Monitoring
%Efficient and Adjustable Run-Time Monitoring Using Dataflow-Guided Filtering
Run-Time Monitoring with Adjustable Overheads \\Using Dataflow-Guided Filtering
}

@@

Recent studies have proposed various parallel run-time monitoring techniques to
improve the reliability, security, and debugging capabilities of computer
systems. However, these run-time monitors can introduce large performance and energy
overheads, especially when performed on programmable cores.
%Traditionally, these overheads have been an
%all-or-nothing cost; monitoring cannot be used if the overheads are considered
%too large.  
In this paper, we introduce a hardware dataflow tracking engine that enables
adjustable overheads through partial monitoring. This allows a trade-off to be
made between monitoring coverage and overhead. This dataflow engine
can also be extended to filter out monitoring operations associated with null
metadata in order to reduce overheads.
% In this paper, we introduce a hardware dataflow tracking engine that can be
% used to filter out unnecessary monitoring and enable adjustable partial monitoring.
% The dataflow engine can identify events with null metadata so that they can
% be filtered out. To further reduce the overhead of monitoring, we propose
% to enable a trade-off between monitoring coverage and overhead by dropping certain
% monitoring operations. For this partial monitoring, the dataflow engine is used
% to track dropped monitoring flows so that false positives can be avoided.
Given this architecture, we investigate how the dropping decisions should be
made for partial monitoring and show that there exist interesting policy
decisions which create a trade-off between closely
matching an overhead target and the coverage that can be achieved.
Our experimental results show that overheads can be reduced significantly 
by trading off coverage. For example, although average overheads for full
monitoring range between 3-4x, the proposed architecture can still
achieve 43-82\% coverage when the slowdown is reduced to 1.5x.
